---
name: "rrtools.tutorial.mpi2020"
title: ReproResearch MPI-SHH 2020
output_dir: "."
author: Clemens Schmid
date: 01/30/2020
output:
  rmdformats::readthedown:
    code_folding: NULL
    self_contained: true
    thumbnails: false
    lightbox: false
css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# The Research Compendium

Definition

## Data + Code + Text

Elements of a research compendium

# R for Reproducible Research

Definition

## R

Basic usage example to transport the idea of a scripting language with addon packages

## RStudio

What is an IDE + Try it out with RStudio Cloud

## R Markdown

Text production with Markdown and R

## Package structure

standardized directory structure

# rrtools

Definition

## Create an R package

```{r}
rrtools::use_compendium("pkgname")
```

## Activate version control

```{r}
usethis::use_git_config(user.name = "Jane Doe", user.email = "jane@example.com")
usethis::use_git()
usethis::browse_github_pat()
usethis::edit_r_environ()
usethis::use_github(protocol = "https", private = FALSE)
```

## Establish the compendium file structure

```{r}
rrtools::use_analysis()
```

## Start writing

Starting to write some text with RMarkdown

# Advanced topics

## README, Code of Conduct and Contribution

```{r}
rrtools::use_readme_rmd()
```

## Licensing

```{r}
usethis::use_mit_license(name = "My Name")
```

## CI/CD

```{r}
rrtools::use_travis(docker = FALSE)
```

## Virtualisation

```{r}
rrtools::use_dockerfile()
```

## Unit tests

```{r}
usethis::use_testthat()
```

# References
